---
title: "Clean Up"
author: "Barry Davis"
date: "June 26, 2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## What's in the box?
cdns_sanitized.csv
: A master list of CDNs and their names

skillsets_sanitized.csv
: A master list of skillset IDs and their names

applications_sanitized.csv
: A master list of application IDs and their names

aggint_application.csv
: Aggregated statistics for applications in 15 minute intervals

aggint_skillset.csv
: Aggregated statistics for skillsets in 15 minute intervals

More files may be added later if additional metrics are needed. 

## Environment
I load Tidyverse to give access to some common and useful packages.
```{r}
library(tidyverse)
```


## Clean Up Objective
The data sets to be used are rather clean as raw data. The application that generates these data sets does a very good job of not letting garbage into these particular sets. Most of the information in the aggregated sources are generated by the application and numerical in nature. The master lists contain names that are input by humans, but in this case, they are already lowercase in the data source. 

The column names are also already relevant. While some are long, they accurately descsribe what the statistic represents. Shortening them further I feel will detract from their usefulness, especially when doing any type of larger calculations.