---
title: "Exploratory Analysis - Call Volume"
author: "Barry Davis"
date: "July 13, 2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE)
```

# Call Volume
In this document we will perform exploratory analysis on Calls Offered, Calls Answered, and Calls Abandoned. 

# Monthly Call Volume
We're going to be looking at specific applications to determine call volume. The applications are directly accessed after selecting a menu option when the client's phone number is dialed.

```{r}
ggplot(primaryApps, aes(x = month(statTimestamp), y = CallsOffered, fill = ApplicationName)) + 
  geom_bar(stat="identity")
ggplot(primaryApps, aes(x = month(statTimestamp), y = CallsAbandoned, fill = ApplicationName)) +
  geom_bar(stat="identity")
ggplot(primarySkills, aes(x = month(statTimestamp), y = CallsAnswered, fill = SkillsetName)) + 
  geom_bar(stat="identity")
```


## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
